\huge Gap formation and stability in non-isothermal protoplanetary disks \large [2014 CITA Summer Student Program]

### 2014-07-24 poster/poster.tex
poster done

            \begin{block}{\Large{Non-linear evolution of gap edge
                  vortices}}
              \justifying
%                  {\bf `lifetime' plot of m=1 for diff beta, snapshots
%                    (before, during, after vortex decay). quote rossby
%                  number when vortices in quasi-steady state}
              Generic evolution independent of $t_\mathrm{cool}$:
              \begin{itemize}
              \item Single vortex in quasi-steady state from vortex merging
              \item Continous vorticity source from disk-planet interaction
                $\to$ vortex intensifies
              \item Vortex dissipates quickly after its Rossby number
                $Ro$ minimizes, due to shocks and/or smoothing out the
                gap edge  
              \end{itemize}
                  \begin{figure}
                    \centering
                    \hfill
                    \begin{minipage}{0.3\textwidth}
                      \includegraphics[width=\textwidth]{Posterfig_Before}
                      \caption{$Ro=-0.16$}
                    \end{minipage}
                    \hfill
                    \begin{minipage}{0.3\textwidth}
                      \includegraphics[width=\textwidth]{Posterfig_During}
                      \caption{$Ro=-0.43$}
                    \end{minipage}
                    \hfill
                    \begin{minipage}{0.3\textwidth}
                      \includegraphics[width=\textwidth]{Posterfig_After}
                      \caption{$Ro=-0.10$}
                    \end{minipage}
                    \hfill
                  \end{figure}

@@

            \begin{block}{\Large{Vortex lifetimes and cooling rate}}
              \justifying
              \begin{itemize}
              \item Vortices typically live longer with increasing cooling time:
              \end{itemize}
              \begin{figure}
                \centering
                \includegraphics[width=\textwidth,clip=true,trim=0cm
                  1.5cm 0cm 1cm]{lifetime_regime1}
              \end{figure}
              \vspace{-1cm}
              \begin{itemize}
              \item However, for very long $t_\mathrm{cool}$ vortex
                lifetimes shorten again:
              \end{itemize}
              \begin{figure}
                \centering
                \includegraphics[width=\textwidth,clip=true,trim=0cm
                  0cm 0cm 1cm]{lifetime_regime2}
              \end{figure}
              \vspace{-2cm}
              \begin{itemize}
              \item A cooling time of $\tilde{\beta}\sim 5$ maximizes
                vortex lifetime (nearly adiabatic)
              \end{itemize}
            \end{block}
            \vfill
            \begin{block}{{\Large Summary}}\justifying
              {\large{\bf
                  The stability of planetary gaps in gaseous
                  protoplanetary disks is affected by disk
                  thermodynamics. A slower cooling rate, which permits
                  more heating, tends to stabilize the system, but
                  also enables longer vortex lifetimes unless the
                  cooling time is extremely long. Our simulations
                  suggest there exists an optimal $t_\mathrm{cool}$
                  that maximizes vortex lifetimes, a result consistent
                  with recent isothermal simulations by Fu et
                  al. (2014,ApJ,788,L41) with variable disk aspect-ratio. 
                }
              }
              \vfill
            \end{block}
          }
          % ---------------------------------------------------------%
          % end the column
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column
  \end{columns}
  \vskip1ex
  %\tiny\hfill\textcolor{ta2gray}{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php}}
  %% \tiny\hfill{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php} \hskip1em}
\end{frame}
\end{document}

>>>>

            \begin{block}{\Large{Non-linear evolution of gap edge
                  vortices}}
              \justifying
%                  {\bf `lifetime' plot of m=1 for diff beta, snapshots
%                    (before, during, after vortex decay). quote rossby
%                  number when vortices in quasi-steady state}
              We include the planet throughout. Generic evolution independent of $t_\mathrm{cool}$:
              \begin{itemize}
              \item Single vortex in quasi-steady state from vortex merging
              \item Continous vorticity source from disk-planet interaction
                $\to$ vortex intensifies
              \item Vortex dissipates quickly after its Rossby number
                $Ro$ minimizes, due to vortex-induced shocks and/or smoothing out the
                gap edge  
              \end{itemize}
                  \begin{figure}
                    \centering
                    \hfill
                    \begin{minipage}{0.3\textwidth}
                      \includegraphics[width=\textwidth]{Posterfig_Before}
                      \caption{$Ro=-0.15$}
                    \end{minipage}
                    \hfill
                    \begin{minipage}{0.3\textwidth}
                      \includegraphics[width=\textwidth]{Posterfig_During}
                      \caption{$Ro=-0.43$}
                    \end{minipage}
                    \hfill
                    \begin{minipage}{0.3\textwidth}
                      \includegraphics[width=\textwidth]{Posterfig_After}
                      \caption{$Ro=-0.05$}
                    \end{minipage}
                    \hfill
                  \end{figure}

@@

            \begin{block}{\Large{Vortex lifetimes and cooling rate}}
              \justifying
              \begin{itemize}
              \item Vortices typically live longer with increasing cooling time:
              \end{itemize}
              \begin{figure}
                \centering
                \includegraphics[width=\textwidth,clip=true,trim=0cm
                  1.5cm 0cm 1cm]{lifetime_regime1}
              \end{figure}
              \vspace{-1cm}
              \begin{itemize}
              \item However, for very long $t_\mathrm{cool}$ vortex
                lifetimes shorten again:
              \end{itemize}
              \begin{figure}
                \centering
                \includegraphics[width=\textwidth,clip=true,trim=0cm
                  0cm 0cm 1cm]{lifetime_regime2}
              \end{figure}
              \vspace{-2cm}
              \begin{itemize}
              \item A cooling time of $\tilde{\beta}\sim 5$ maximizes
                vortex lifetime (thick line)
              \end{itemize}
            \end{block}
            \vfill
            \begin{block}{{\Large Summary}}\justifying
              {\large{\bf
                  The stability of planetary gaps in gaseous
                  protoplanetary disks is affected by disk
                  thermodynamics. A slower cooling rate, which permits
                  more heating, tends to stabilize the system, but
                  also enables longer vortex lifetimes unless the
                  cooling time is extremely long. Our simulations
                  suggest there exists an optimal $t_\mathrm{cool}$
                  that maximizes vortex lifetimes, a result consistent
                  with recent isothermal simulations by Fu et
                  al. (2014,ApJ,788,L41) with variable disk aspect-ratio. 
                }
              }
              \vfill
            \end{block}
          }
          % ---------------------------------------------------------%
          % end the column
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    % ---------------------------------------------------------%
    % end the column
  \end{columns}
  \vskip1ex
  %\tiny\hfill\textcolor{ta2gray}{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php}}
  %% \tiny\hfill{Created with \LaTeX \texttt{beamerposter}  \url{http://www-i6.informatik.rwth-aachen.de/~dreuw/latexbeamerposter.php} \hskip1em}
\end{frame}
\end{document}
